\cvsection{Experience}
\vspace*{-3mm}
\begin{cventries}
\cventry
    {Developer (CO-OP)}
    {RBC HR Compensation Technology, Toronto ON}
    {}
    {Jan. 2019 - Present}
    {
      \begin{cvitems}
        \item {Worked on internal applications angular Front-end and Spring Back-end}
        \item {Created new components and APIs for the admin portal for the application}
      \end{cvitems}
    }
    \vspace*{-3mm}
\cventry
    {Full-Stack Software Developer (CO-OP)}
    {Verto Inc, Toronto ON}
    {}
    {May. 2018 - Dec.2018}
    {
      \begin{cvitems}
        \item {Developed and maintained the core applications RightPath Engage(Angular 6), RightPath Flow (Ruby on Rails), Veritas(Python)}
        \item{ worked with postgreSQL for the main database for all 3 applications }
        \item { Developed core functionality for the two applications using Ruby on Rails and Angular 6 }
        \item { worked with Python to develop core functionality for a new application }
        \item { Worked with an established team of developers to complete tasks and interact with project manager }
        \item { worked with several other APIs to connect to the applications to send out emails and Sms updates }
      \end{cvitems}
    }
    \vspace*{-3mm}
  \cventry
    {Summer Temporary Assistant (4 Months CO-OP)}
    {Ryerson University - Undergraduate Admissions, Toronto ON}
    {}
    {Jun. 2017 - sep. 2017}
    {
      \begin{cvitems}
        \item {Increased usability and productivity by developing an equipment rental system using Forms and Google Scripts.}
        \item {Automated generation and modification of excel reports by created multiple VBA macro applications for Excel and Word}
        \item{increased efficiency by 3-5 min for each report and reduced human error.}
        \item {Created executable Java programs to search through file systems and gather student information.}
        \item{Communicated with current applicants and assisted them with their applications via emails.}
      \end{cvitems}
    }
    
 
\end{cventries}
\vspace*{-6mm}