\cvsection{}
\begin{cvletter}
\CVstartWinterFull{Intelliware Development Inc.} {Toronto, ON}
 
It is with great pleasure that I am submitting my application for Software Development Intern at Intelliware Development as listed on Ryerson Co-op portal. As I have completed my third year and third work term towards my BSc. Computer Science Co-op Honours at Ryerson University. I am drawn to this position because it combines my passion for technology with my developing skills. Based on my experience gained through various work terms and my past academic projects I am qualified for this position.

Working as a Full stack Software Developer at Verto Inc. has excelled my development skills. I have worked with Ruby on Rails, Angular and Python to maintain and further develop the core applications RightPath Flow, RightPath Engage, Veritas and which are distributed and used in various hospitals throughout Ontario. The two apps are interconnected via API requests, the apps also use other APIs for various features. Both applications use PostgreSQL for their database and use rails active record to retrieve and run queries with the applications. I worked with a team of developers and project manager to complete tasks and stories.

While working as a Summer Temporary Assistant CO-OP at Ryerson University Undergraduate Admissions I developed multiple web applications to be used for daily report automation which included creating multiple VBA Macros. I also modified multiple XML files to make them compatible with the new scripts and programs. Some projects include: a fully automated Google Drive user removal system using Google App Scripts and JavaScript and file parsing multiple executable Java programs.

Throughout my academic career, I have had valuable experience in: JAVA, C, SHELL/BASH, Python and Assembly
language. I can confidently navigate through Linux/Unix via terminal. I have valuable experience with different software and operating systems: Windows 7, 8, 10, Mac OS, Linux, Git, and MS Office. 

I have created multiple programs and applications for course projects. One of which include a SQL based database system created from scratch, creating ER diagram with full relations then coded the tables based on the diagram. I have experience constructing multiple queries to test the database. Finally developing a bash script text based program to run all the commands via ssh into the server. Some outside projects include NoStressPark created at Boston Hacks 2018 is an IOS app created to easily find parking in the city of Boston. App functions using 2 APi calls one to Shine to get the near by spots and then to city of Boston's own data api to get the meter info and display it for the user. I believe
these experiences and passionate would make me a great asset for Intelliware.

\CVend
\end{cvletter}